### 2021-09-13 paper/output/document/paper32.tex
finished application tests for Kroy - next steps are to port learnings to the naive interpretation, and move on to metaethical tests

for a specific person $p$, then it must be prohobited for all people. This test case also revealed a 

@@

  Free variable:
    p = $s_1$
  Skolem constant:
    $\lambda$w. p = ($\lambda$x. $\_$)($i_1$ := $s_1$) $\color{black}$%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Kroy's formulation also fails to show that if not everyone can lie, then lying is prohibited. 
      There may be an issue here with our representation of lying not being universal. Specifically, 
      the FUL is violated if it's not $possible$ for everyone to simultaneously lie, but the abbreviation 
      above merely represents that fact that not everyone does, in fact, simultaneously lie. It's entirely
      possible that everyone can simultaneously lie, but for some reason, maybe out of some moral sense, 
      do not. Let's test a more accurate version of the failure of the universalizability test.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
We want to represent the sentence, call it $S$ $\longleftrightarrow$ ``At all worlds, it is not possible that everyone lies simultaneously.
      Representing this sentence requires that we apply a universal quantifier inside the possible operator,
      something that DDL does not support as-is. There are two options here. (1) We can pull the universal outside
      the diamond operator, resulting in the sentence ``At all worlds, for all people, it is not possible that 
      they lie." This isn't $\textbf{really}$ the same as $S$. (2) We can define universal and existential 
      operators that quantify over DDL formulae to actually represent $S$ as we want to. I am going to 
      try to implement (2), borrowing from \cite{gewirth}'s extension of Carmo and Jones' DDL. This 
      will also be useful when creating my own formalization of the categorical imperative. MOVE THIS TO NAIVE%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
abbreviation lying not possibly universal::bool where "lying not possibly universal longleftrightarrow forall w. not (diamond (forall p. lie(p)))w)"%
\end{isamarkuptext}\isamarkuptrue%
%
\isamarkupcmt{The formula above reads, "At all worlds, it is not possible%
}%
\begin{isamarkuptext}%
something more sophisticated? like the nazi example?%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
maybe trolley problem/self driving car thing%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Metaethical Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
\ \ \isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:

@@

%:%554=266%:%

@@

%:%556=268%:%
%:%557=269%:%
%:%558=270%:%
%:%559=271%:%

@@

%:%566=274%:%
%:%569=278%:%
%:%573=280%:%
%:%582=282%:%
%:%592=284%:%
%:%593=284%:%
%:%594=285%:%
%:%595=286%:%
%:%596=286%:%
%:%598=286%:%
%:%602=286%:%
%:%603=286%:%
%:%605=287%:%
%:%606=288%:%
%:%607=289%:%
%:%608=290%:%
%:%609=290%:%
%:%611=291%:%
%:%619=291%:%
%:%620=292%:%
%:%621=293%:%
%:%622=293%:%
%:%623=294%:%
%:%624=295%:%
%:%625=296%:%
%:%626=296%:%
%:%628=296%:%
%:%632=296%:%
%:%633=296%:%
%:%635=297%:%
%:%636=298%:%

@@

%:%638=300%:%

@@

%:%641=301%:%
%:%642=302%:%
%:%650=302%:%
%:%651=303%:%
%:%652=304%:%

@@

%:%656=307%:%

@@

%:%659=307%:%
%:%663=307%:%
%:%673=309%:%
%:%677=313%:%
%:%681=315%:%
%:%685=317%:%
%:%694=319%:%
%:%706=321%:%

>>>>

for a specific person $p$, then it must be prohibited for all people. This test case also revealed a 

@@

    p = $s_1$
  Skolem constant:
    $\lambda$w. p = ($\lambda$x. $\_$)($i_1$ := $s_1$) $\color{black}$%
Kroy's formulation also fails to show that if not everyone can lie, then lying is prohibited. 
      There may be an issue here with our representation of lying not being universal. Specifically, 
      the FUL is violated if it's not $possible$ for everyone to simultaneously lie, but the abbreviation 
      above merely represents that fact that not everyone does, in fact, simultaneously lie. It's entirely
      possible that everyone can simultaneously lie, but for some reason, maybe out of some moral sense, 
      do not. Let's test a more accurate version of the failure of the universalizability test.%
We want to represent the sentence, call it $S$ $\longleftrightarrow$ ``At all worlds, it is 
      not possible that everyone lies simultaneously." Consider the two abbreviations below.%
\ everyone{\isacharunderscore}lies{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ {\isachardoublequoteopen}everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This represents the term ``all people lie". Naively, we might think to represent this as $\forall p. lie(p)$.
In HOL, the $\forall$ operator has type $('a\rightarrow bool) \rightarrow bool$, where $'a$ is a polymorphic
type representing the type of the argument to $\forall$. This is because the universal quantifier binds 
the argument of the term given to it, such that it turns an open term into a closed term. In the given example, 
$\forall$ has the type $(s \rightarrow bool) \rightarrow bool$, so it can only be applied to a formula 
of type $s \rightarrow bool$. In the abbreviation above, we're applying the quantifier to the sentence 
$lie(p) w$ for any arbitrary $w$, so the types cohere.%
\isamarkupcmt{The term above is true for a set of worlds $i$ (recall that a term is true at a set of worlds) 
such that, at all the worlds $w$ in $i$, all people at $w$ lie.%
\ lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}bool\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possibly{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}{\isacharparenleft}{\isasymdiamond}everyone{\isacharunderscore}lies\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Armed with \isa{everyone{\isacharunderscore}lies\ {\isasymequiv}\ {\isasymlambda}w{\isachardot}\ {\isasymforall}p{\isachardot}\ lie\ p\ w}, it's easy to represent the sentence $S$. The abbreviation above 
reads, ``At all worlds, it is not possible that everyone lies."%
\ lying{\isacharunderscore}prohibited{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}possible{\isacharunderscore}universal\ {\isasymlongrightarrow}\ \ {\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}lie{\isacharparenleft}p{\isacharparenright}{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{$\color{blue}$Nitpick found a counterexample for card i = 1 and card s = 2:

  Free variables:
    $lying\_not\_possible\_universal$ = True
    p = $s_1$ $\color{black}$%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Even with the stronger assumption that it's not possible for everyone to lie 
simultaneously, Kroy's formulation is still not able to show that lying is prohibited for an arbitrary
person. That's a problem! WHY IS THIS HAPPENING%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Metaethical Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
\ \ \isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:

@@

@@

%:%556=267%:%
%:%558=268%:%
%:%559=269%:%
%:%560=270%:%
%:%561=271%:%
%:%562=272%:%

@@

%:%564=274%:%
%:%565=274%:%
%:%567=275%:%
%:%568=276%:%
%:%569=276%:%
%:%570=277%:%
%:%571=278%:%
%:%572=278%:%
%:%574=279%:%
%:%575=280%:%
%:%576=280%:%
%:%577=281%:%
%:%578=282%:%
%:%579=282%:%
%:%580=283%:%
%:%581=284%:%
%:%582=284%:%
%:%584=284%:%
%:%588=284%:%
%:%589=284%:%
%:%591=285%:%
%:%592=286%:%
%:%593=287%:%
%:%594=288%:%
%:%595=289%:%
%:%605=291%:%
%:%606=292%:%
%:%607=293%:%
%:%616=295%:%
%:%626=297%:%
%:%627=297%:%
%:%628=298%:%
%:%629=299%:%
%:%630=299%:%
%:%632=299%:%
%:%636=299%:%

@@

@@

%:%640=301%:%
%:%641=302%:%
%:%642=303%:%
%:%643=303%:%
%:%645=304%:%

@@

%:%656=306%:%

@@

%:%658=308%:%
%:%659=309%:%
%:%660=309%:%
%:%662=309%:%
%:%666=309%:%
%:%667=309%:%
%:%669=310%:%
%:%670=311%:%
%:%671=312%:%
%:%672=313%:%
%:%673=313%:%
%:%675=314%:%
%:%676=315%:%
%:%684=315%:%
%:%685=316%:%
%:%686=317%:%
%:%687=317%:%
%:%688=318%:%
%:%689=319%:%
%:%690=320%:%
%:%691=320%:%
%:%693=320%:%
%:%697=320%:%
%:%707=322%:%
%:%711=326%:%
%:%715=328%:%
%:%719=330%:%
%:%728=332%:%
%:%740=334%:%
